\begin{eabstract}
These days, penetration of mobile phone in Japan is over a 100 percent. Especially, penetration of smart phone in Japan is over 50 percent. All of the Japanese people have a mobile phone and half of Japanese people have a smart phone. So we are not able to live without the smartphone.
Why are smart phones spreading? This is because smart phone is convenient. We can do various things such as playing a game, watching a movie, web browsing, doing schedule management doing data management using SNS application, seeing the map, chat, and so on at using smart phones. We were not able to do these actions without PCs so far. 
suggested futuristic smart phone applications by the joint development of three universities, FUTURE UNIVERSITY HAKODATE, KANAGAWA INSTITUTE OF TECHNOLOGY, NAGASAKI UNIVERSITY by this project.
We developed applications using development process of waterfall. First, we suggested application's idea. This year, we suggested two application's idea. Their are "Cool Japanimation" and "Rhyth/Walk". Second, we write development documentation. Third, we develop applications. This year, we developed "Cool Japanimation" at Android and HTML5, "Rhyth/Walk" at Android and iOS. Last, we do the test for application. Moreover, we consider business model because we want to suggest application which many people use. 
We could learn the development process when we use this development process. This was the project purpose. 
\\[5mm]
\bunseki{Kazuki Iwata(Future University Hakodate)}
\end{eabstract}
